{\fontfamily{ptm}\selectfont Reading Notes}

### 2025-05-06 Notebook LaTEX/Formalized Notes/Notes 2025 03/main.tex
>w<, changes

    \begin{theorem}[weakly convex generic proximal gradient inequality]\label{thm:pg-ineq-wcnvx-generic}\;\\

@@

@@

            If in addition, the sequence $(\alpha_k)_{k \ge 0}$ has $\alpha_0 = 1$ and it is initialized with $x_0=x_0 = T_{1/L_0, f, g}x_{-1}$ for some $x_{-1} \in\RR^n$ and there exists $x^+$ which is a minimizer of $F$. 

@@

            The following intermediate results are in order for the proof. 

@@

                \item[(a)]

@@

@@

        This section introduces two variants of line search method used to enhance the accelerated proximal gradient methods in the literatures to demonstrate Definition \ref{def:generic-mapg-ls}. 

@@

                    \begin{tabular}{lcl}
                        $f : \RR^n \rightarrow \RR$ && Convex Lipschitz smooth\\ 
                        $g: \RR^n \rightarrow \overline \RR$  &&  Convex function with Proximal operator\\ 
                        $x \in \RR^n$ && Vector\\
                        $v \in \RR^n$ && Vector\\
                        $L \in \RR$ && $L > 0$\\
                        $\alpha \in \RR$  && $\alpha \in (0, 1]$

@@

                    \textbf{Function ChamBT}($f, g, x, v, L, \alpha, L_{\min}, \rho$)

@@

                    \textbf{Function BeckMono}($f, g, x, v, L, L_{\min}, \rho, \alpha$)

@@

    \section{Practical enhancement}
        In this section, we provide results for the faster convergence rate of examples listed from the previous section. 
    \section{Nonconvex convergence}

    \section{Restarting with gradient and function values}

>>>>

    \begin{theorem}[weakly convex generic proximal gradient inequality]\;\label{thm:pg-ineq-wcnvx-generic}\\

@@

            The sequence has explicit update formula: 
                \alpha_k = 
                \frac{1}{2}
                    \alpha_{k - 1}\sqrt{\alpha_{k -1}^2 + 4 \rho_{k - 1}} - \alpha^2_{k - 1}

@@

            If in addition, the sequence $(\alpha_k)_{k \ge 0}$ has $\alpha_0 = 1$ and, it is initialized with $x_0=x_0 = T_{1/L_0, f, g}x_{-1}$ for some $x_{-1} \in\RR^n$ and there exists $x^+$ which is a minimizer of $F$. 

@@

            The following intermediate results will be used in the proof. 
            We stated prior to the proof for a sleeker exposition. 

@@

                \item[(a)] From Definition \ref{def:generic-mapg-ls}, the gradient mapping satisfies for all $k \ge 1$ that $\Vert \mathcal G_{1/L_k} y_k\Vert = L_k\alpha_k \Vert v_k - v_{k - 1}\Vert$.
                \item[(b)] We have $(a_k)_{k \ge 1}$ satisfying $\forall k \ge 1$ that $(1 - \alpha_k)\rho_{k - 1} = \alpha_k^2/\alpha_{k - 1}^2$ from the statement hypothesis. We assumed $\alpha_0 = 0, \beta_0 = 1$, $x^+$ is a minimizer of $F$. Then using these it has for all $k \ge 0$ it has $\frac{\alpha_k}{\sqrt{\beta_k L_0}}\Vert x^+ - v_k\Vert \le \Vert x^+ - v_0\Vert$. 
                \item[(c)] The sequence $(\alpha_k)_{k \ge 0}$ has $(1 - \alpha_k)\rho_{k - 1} = \alpha_k^2/\alpha_{k - 1}^2$ from the statement hypothesis so $\alpha_k/\alpha_{k - 1} = \sqrt{\rho_{k - 1}(1 - \alpha_k)}$ for all $k \ge 1$. 
                \item[(d)] The definition of the sequence $(\beta_k)_{k \ge 0}$ stated in the statement hypothesis. 

@@

            From these intermediate results, the convergence can be derived. 
            From (a) it has for all $k \ge 0$: 
                \Vert \mathcal G_{L_k} y_k\Vert 
                &= L_k\alpha_k \Vert v_k - v_{k - 1}\Vert
                L_k\alpha_k(\Vert v_k - x^+\Vert + \Vert v_{k - 1} - x^+\Vert)
                &\underset{\text{(b)}}{\le} 
                L_k \alpha_k \left(
                    \frac{\sqrt{\beta_kL_0}}{\alpha_k}\Vert x^+ - v_0\Vert
                    \frac{\sqrt{\beta_{k - 1}L_0}}{\alpha_{k - 1}}\Vert x^+ - v_0\Vert
                &= L_k\sqrt{L_0} \left(
                    \sqrt{\beta_k}
                    \frac{\alpha_k\sqrt{\beta_{k - 1}}}{\alpha_{k - 1}}
                \right)\Vert x^+ - v_0\Vert
                &= \sqrt{\beta_k L_0}L_k \left(
                    \frac{\alpha_k}{\alpha_{k - 1}}\sqrt{\frac{\beta_{k - 1}}{\beta_k}}
                \right)\Vert x^+ - v_0\Vert
                &\underset{\text{(d)}}{=} \sqrt{\beta_k L_0}L_k \left(
                    \frac{\alpha_k}{\alpha_{k - 1}}
                    \left((1 - \alpha_k)\max(1, \rho_{k - 1}L_k L_{k - 1}^{-1})\right)^{-1/2}
                \right)\Vert x^+ - v_0\Vert
                &\underset{\text{(c)}}{=} 
                \sqrt{\beta_k L_0}L_k \left(
                    ((1 - \alpha_k)\rho_{k - 1})^{1/2}
                    \left((1 - \alpha_k)\max(1, \rho_{k - 1}L_k L_{k - 1}^{-1})\right)^{-1/2}
                \right)\Vert x^+ - v_0\Vert
                \sqrt{\beta_k L_0}L_k \left(
                    \left(\rho_{k - 1}^{-1}\max(1, \rho_{k - 1}L_k L_{k - 1}^{-1})\right)^{-1/2}
                \right)\Vert x^+ - v_0\Vert
                \sqrt{\beta_k L_0}L_k \left(
                    \max(\rho_{k - 1}^{-1}, L_k L_{k - 1}^{-1})^{-1/2}
                \right)\Vert x^+ - v_0\Vert
                \sqrt{\beta_k L_0}L_k \left(
            Now, \textbf{let's proof intermediate results (a)}. 
            From the definition of GMAPG it has 
                y_k &= \alpha_k v_{k - 1} + (1 - \alpha_k)x_{k - 1}
                v_{k - 1} = \alpha_k^{-1}(y_k - (1 - \alpha_k)x_{k - 1}). 
            Using the above, and definition of GMAPG, it yields 
                v_k - v_{k - 1} &= 
                (x_{k - 1} + \alpha_k^{-1}(\tilde x_k - x_{k - 1})) - \alpha_k^{-1}(y_k - (1 - \alpha_k)x_{k - 1})
                x_{k - 1} + \alpha_k^{-1}(\tilde x_k - x_{k - 1})
                - \alpha_k^{-1}y_k + (\alpha_k^{-1} - 1)x_{k - 1}
                &= \alpha_k^{-1}(\tilde x_k - x_{k - 1}) - \alpha_k^{-1}y_k + \alpha_k^{-1} x_{k - 1}
                &= \alpha_k^{-1}\tilde x_k - \alpha_k^{-1} y_k 
                = \alpha^{-1}_k(\tilde x_k - y_k) = \alpha_k^{-1}(T_{L_k} y_k - y_k)
                &= -\alpha_k^{-1}L_k^{-1}(\mathcal G_{L_k}(y_k)). 
            \textbf{We now prove result (b)}. 
            The base case $k = 1$ is verified by the assumption that $x_0 = v_0 = T_{L_0} x_{-1}$. 
            Apply the proximal gradient inequality with $x^+$ as a minimizer it yields: 
                - \frac{L_0}{2}\Vert x^+ - v_0\Vert^2 + 
                &= \frac{L_0}{2}\left(
                    \Vert x^+ - x_{-1}\Vert- \Vert x^+ - v_0\Vert 
            Because $\beta_0 = \alpha_0 = 1$, the base case holds. 
            For all $k \ge 1$, we consider the convergence claim and use the assumption that $x^+$ is a minimizer of $F$ so, it has from Theorem \ref{thm:gmapg-ls-convergence} that 
                0 &\le \frac{L_0\beta_k }{2}\Vert x^+ - x_{-1}\Vert^2 
                - F(x_k) + F(x^+) - \frac{L_k\alpha_k^2}{2}\Vert x^+ - v_k\Vert^2
                \frac{L_0\beta_k }{2}\Vert x^+ - x_{-1}\Vert^2 
                - \frac{L_k\alpha_k^2}{2}\Vert x^+ - v_k\Vert^2
                &= \frac{\alpha_k^2L_k}{2}\left(
                    \frac{\beta_k}{\alpha_k^2L_0}
                    \Vert x^+ - x_{-1}\Vert^2 
                    - \Vert x^+ - v_k\Vert^2
                \Vert x^+ - x_{-1}\Vert - \frac{\alpha_k}{\sqrt{\beta_k L_0}}\Vert x^+ - v_k\Vert. 

@@

        This section will introduce various type of implementations that can be fitted into GMAPG in Definition \ref{def:generic-mapg-ls}. 

@@

                    \begin{tabular}{ll}
                        $f : \RR^n \rightarrow \RR$ & Convex Lipschitz smooth\\ 
                        $g: \RR^n \rightarrow \overline \RR$  &  Convex function with Proximal operator\\ 
                        $x \in \RR^n$ & Vector\\
                        $v \in \RR^n$ & Vector\\
                        $L \in \RR$ & $L > 0$\\
                        $\alpha \in \RR$  & $\alpha \in (0, 1]$

@@

                    % \textbf{Function ChamBT}($f, g, x, v, L, \alpha, L_{\min}, \rho$)
                    \textbf{Function ChamBT input: }
                    \begin{tabular}{ll}
                        $f:\RR^n \rightarrow \RR$ & Convex Lipschitz smooth\\ 
                        $g:\RR^n \rightarrow \overline\RR$ & Convex with Proximal Operator\\ 
                        $x\in \RR^n$ & Vector\\
                        $v\in \RR^n$ & Vector\\
                        $\alpha \in \RR$ & Vector\\
                        $L\in \RR$ & Number, $L > 0$ \\
                        $L_{\min} \in \RR$ & Number, $L_{\min} > 0$\\
                        $\rho \in \RR$ & Number, $\rho \in (0, 1)$\\

@@

                    % \textbf{Function BeckMono}($f, g, x, v, L, L_{\min}, \rho, \alpha$)
                    \textbf{Function BeckMono Input:}
                    \begin{tabular}{ll}
                        $f: \RR^n \rightarrow \RR$ & \\
                        $g: \RR^n \rightarrow \overline \RR$ & \\
                        $\tilde x \in \RR^n$ & \\
                        $x \in \RR^n$ & 

@@

    \section{Practical enhancement from the Nesterov's Monotone Variant}
        In this section, we provide results for the faster convergence rate of examples listed from the previous section. 
    \section{Restarting with function values}
    \section{Applying them to large scale LP}
    \section{Nonconvex convergence}
